Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/splitting.tex
Incorporate Carlo's comments into 4.4.

Rather than attempt global optimization of the outputs of splitting,
we instead introduce world \bbonep\ and use the type system to
statically prove terms contain no second stage computations.  In these
situations, splitting is trivial---splitting $\pure e$ terms yields a
unit resumer.

>>>>

Rather than attempt global optimization of the outputs of splitting,
we instead leverage the type system to indicate when a term contains
no second-stage computations by adding a third world \bbonep\ whose
terms are purely first stage.  While not necessary for ordinary staged
term evaluation (\ref{sec:stagedsemantics}), this annotation is
particularly useful for splitting. Specifically, splitting $\pure e$
terms trivially yields a unit resumer.
